FFI Is Not Enough. We Need Dependent Types.

### 2013-06-06 papers/sle2013/sle2013.tex
Fix sle abstract

\title{FFI Is Not Enough. We Need Dependent Types}
\titlerunning{Dependent Types Rock}

@@

\begin{abstract}
JavaScript sucks. It is a known fact. Several other programming languages can target JavaScript as a back-end,
alleviating developers from the burden of writing and maintaining JavaScript code. The Web browser APIs,
which are needed to interact with a Web page, are designed for JavaScript, making it challenging to expose them in a
statically typed language. Indeed, existing statically typed languages either loose control or loose type safety.
How to give users the same level of control as if they were using the native Web APIs, but in a statically typed and
convenient way? This article shows how dependent type systems can help.
\keywords{Dependent Types}
\end{abstract}

>>>>

\title{FFI Is Not Enough. We Need Dependent Types.}
\titlerunning{Dependent Types Rock}

@@

\begin{abstract}
Several programming languages can target JavaScript as a back-end, giving developers programming language features
that are absent from JavaScript, such as static typing. However, the Web browser APIs, which are needed to interact
with a Web page, are designed for JavaScript, making it challenging to expose them in a statically typed language.
Indeed, existing statically typed languages exposing Web browser APIs either break type safety or give developers
less control than if they were using JavaScript. This article shows how to expose Web browser APIs in Scala in a
type safe way while keeping the same level of control as with native APIs. We use advanced type system features such
as dependent types and functional dependencies.
\keywords{Dependent Types}
\end{abstract}
